%-------------------------
% Resume in Latex
% Author : Jayvardhan Rathi
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://linkedin.com/in/rathi406}{\Large Jayvardhan Rathi}} & \href{mailto:rathi406@gmail.com}{rathi406@gmail.com} \\
  SOFTWARE DEVELOPER & +1-123456789 \\
  \href{https://jayvardhanrathi.tech/}{jayvardhanrathi.tech} & \href{https://github.com/ComputerScientist-01}{ComputerScientist-01} \\
  & \href{https://linkedin.com/in/rathi406}{LinkedIn: rathi406} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SRM Institute of Science and Technology (SRMIST)}{Chennai, Tamil Nadu}
      {B.TECH in Computer Science and Engineering; CGPA: 8.96}{Jun. 2019 - May. 2023}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {HSBC}{Pune, Maharashtra, India}
      {Software Developer (Full-time)}{Aug. 2023 - Present}
      \resumeItemListStart
        \resumeItem{Collaborated with Senior Developers and Business Analysts}
          {Contributed to both tactical and strategic solutions for data ingestion in liquidity reporting, enhancing the efficiency and accuracy of financial data processing. Worked closely with senior professionals to align technical implementations with business goals, ensuring the delivery of high-impact solutions.}
        \resumeItem{Hands-on Experience in Big Data Technologies}
          {Gained in-depth experience with Apache Spark and Apache Airflow while working on complex projects within the Big Data ecosystem. Played a key role in optimizing data processing pipelines, which significantly improved data throughput and reduced latency.}
        \resumeItem{Application Enhancement of "MAGNUS" Platform}
          {Led the development of new features and optimizations using Apache Airflow, including the creation of new DAGs (Directed Acyclic Graphs) that streamlined workflow automation. These enhancements increased the platform’s efficiency by reducing manual interventions and accelerating task execution times.}
        \resumeItem{Technical Environment}
          {Operated in a dynamic technical environment involving Linux, Java, Python, Jenkins, Ansible, and JIRA. Contributed to multiple stages of the software development lifecycle, from design and coding to deployment and maintenance, ensuring the robustness and reliability of the software solutions.}
        \resumeItem{Skills Acquired}
          {Developed strong proficiency in Apache Spark, Apache Airflow, Python, REST APIs, and Pandas. Applied these skills to real-world projects, leading to significant improvements in data processing capabilities, automation, and overall system performance.}
      \resumeItemListEnd

    \resumeSubheading
      {TECHNOCOLABS}{Remote}
      {Python Developer (Internship)}{July 2020 - Aug. 2020}
      \resumeItemListStart
        \resumeItem{Project Overview:}
          {Created a robust full-stack weather application that provides detailed real-time weather information, including temperatures, wind speeds, and humidity levels, by leveraging the OpenWeatherMap API for accurate data retrieval.}
        \resumeItem{Development Approach: }
          {Employed the Iterative Enhancement Model to systematically refine and enhance the application through weekly tasks}
        \resumeItem{Key Skills Acquired:} 
        {PyOWM for weather data retrieval, Streamlit for building interactive web interfaces, and Matplotlib for data visualization.}

        \resumeItem{Tech Stack}
          {PyOWM API, Python, Streamlit, Plotly.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubheading
    {Redfin Real Estate Data Analytics ETL Pipeline}{Remote}
    {Data Engineering Project}{August 2024}
    \resumeItemListStart
        \resumeItem{Objective}
            {Architected and implemented a fully automated ETL pipeline, revolutionizing how real estate data is processed, stored, and analyzed, leading to more timely and actionable insights.}
        \resumeItem{Data Extraction}
            {Successfully connected to Redfin’s data center and extracted large volumes of real estate data using Python, ensuring accuracy and completeness for downstream processes.}
        \resumeItem{Data Transformation}
            {Utilized Pandas to cleanse and transform raw data into a structured format, optimizing it for analysis and storage, thereby improving data quality and accessibility.}
        \resumeItem{Data Loading}
            {Strategically loaded both raw and transformed datasets into Amazon S3 buckets, enabling scalable and secure data storage while supporting future data growth.}
        \resumeItem{Automation}
            {Integrated Snowpipe with the ETL pipeline, enabling real-time loading of transformed data into Snowflake upon arrival in S3. This automation streamlined data workflows and reduced manual intervention.}
        \resumeItem{Visualization}
            {Connected Power BI to the Snowflake data warehouse, creating dynamic dashboards that empowered stakeholders with real-time insights into market trends, driving data-informed decision-making.}
        \resumeItem{Tools \& Technologies}
            {Apache Airflow, Python, Pandas, AWS S3, Snowflake, Snowpipe, Power BI.}
    \resumeItemListEnd
\resumeSubHeadingListEnd




%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Programming Languages:} C++, Python, SparkSQL, MySQL}
      \hfill
      \item{
      \textbf{Tools \& Frameworks:} Streamlit, Matplotlib, Numpy, Apache Spark, Apache Airflow,JIRA,Jenkins,MS Excel }
      \hfill
      \item{\textbf{Domain level skills} Data Engineering,Data Ingestion,Data Structures,Prompt Engineering}
  \resumeSubHeadingListEnd

  
%-------------------------------------------



%-----------ACHIEVEMENTS-----------------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubItem{Secure Code warrior - Orange Belt - Python API}{Demonstrated secure coding skills through tailored assessments that target specific security issues ensuring compliance and reducing risks}
    \resumeSubItem{Database Foundations - Oracle}{Learnt database design techniques , designed databases using a modelling tool , were introduced to SQL to implement and query databases using hands-on activities}
    \resumeSubItem{Python (Basic) Certificate}{Certified in Python fundamentals, including data types, control flow, collections, and object-oriented programming, demonstrating proficiency in essential programming concepts}
  \resumeSubHeadingListEnd

%-----------TECHNICAL BLOGGING-----------------
\section{Technical Blogging}
  \resumeSubHeadingListStart
    \resumeSubItem{Technical Creator, CRiO.DO (Remote)}{Authored a comprehensive technical tutorial on developing a Weather Forecasting App, guiding users through visualizing weather data using OpenWeatherMap APIs and Streamlit.Covered key skills such as PyOWM, Streamlit, Matplotlib, and data visualization, providing in-depth references and project flow diagrams for easier understanding.}
    
  \resumeSubHeadingListEnd



\end{document}
